A framework for mentored data science research

### 2019-12-09 Rmd/methods.Rmd
updated methods

@@

Our framework broadens statistical computing by including the emerging areas of
social media data analysis, sentiment analysis, and topic modeling. 
Both students used Twitter tweets, which we accessed through a Twitter 
streaming API.

>>>>

```{r t1, echo = FALSE}
library(magrittr)
step <- c(rep("Question formulation", 3),
          rep("Data acquisition", 3), 
          rep("Data analysis and visualization", 2), 
          rep("Presentation and communication", 3)
)
details <- c("List ideas", "Prioritize ideas", "Check data availability",
             "Download tweets and other data", "Parse tweet JSON", "Organize data as times series",
             "Exploratory plots", "Summary statistics",
             "Interpret and summarize graphs and summary statistics", "Prepare written materials and figures", "Share findings as posters, slides, and reports"
             )
tibble::tibble(step, details) %>%
#  dplyr::group_by(step) %>%
  gt::gt() %>%
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "lightcyan"),
      gt::cell_text(style = "italic")
      ),
    locations = gt::cells_data(
      columns = dplyr::vars(details),
      rows = step == "Question formulation"
      )
  ) %>%
    gt::tab_style(
    style = list(
      gt::cell_fill(color = "pink"),
      gt::cell_text(style = "italic")
      ),
    locations = gt::cells_data(
      columns = dplyr::vars(details),
      rows = step == "Data acquisition"
      )
  ) %>%
  gt::tab_header(
    title = gt::md("Framework Overview"), subtitle = "xxx"
  ) %>%
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "apricot"),
      gt::cell_text(style = "italic")
      ),
    locations = gt::cells_data(
      columns = dplyr::vars(details),
      rows = step == "Data analysis and visualization"
      )
  ) %>%
  gt::as_latex()
```

@@

Our framework broadens statistical computing by including the emerging areas of
social media data analysis, sentiment analysis, and topic modeling. 
Both students used Twitter tweets, which we accessed through a Twitter 
streaming API. One student chose to apply topic modeling to tweets. 
The other elected to apply sentiment analysis to daily 
tweet collections. By using these methods, sentiment analysis and 
topic modeling, students learned an aspect of text analysis that 
is not taught in traditional statistics courses.
